\documentclass[11pt, a4paper, final]{resume}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% CV ANGLAIS %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{setspace}
\usepackage{needspace} % in the preamble


%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

% for debugging purposes
%\overfullrule=5pt

\renewcommand{\baselinestretch}{1}

% publication{authors}{title}{conference description}
\newcommand*{\publication}[3]{{
	\needspace{4\baselineskip} % ensure at least 4 lines fit
	\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}
		{#1}\\[-0.3em]
		{\textit{#2}}\\[-0.3em]
		{#3}
}}


\begin{document}


	\begin{center}
		\namestyle{Médéric Fourmy}  \\
		\vspace{0.3cm}
		\emailstyle{\faEnvelope~mederic.fourmy@gmail.com} ~~
		\href{https://mederic.fourmy.github.io/}{\emailstyle{\faGlobe~mederic.fourmy.github.io}} ~~
		\href{https://github.com/MedericFourmy/}{\emailstyle{\faGithub~Github}}  ~~
		\href{https://www.linkedin.com/in/mederic-fourmy-738aa3110/}{\emailstyle{\faLinkedin~LinkedIn}}  ~~
		\href{https://scholar.google.com.au/citations?user=eBMti0cAAAAJ&hl=en}{\emailstyle{\faGraduationCap~Google Scholar}}
	\end{center}
	\vspace{0.2cm}
	I am a postdoc researcher at CIIRC-CTU in Prague, working at the interface between model-based
	robotics control and computer vision. My work focuses on developing robust and generalizable object pose estimation methods, robot optimal control for grasping and visual servoing
	tasks. I am looking for a research scientist/engineer position in robotics/AI.

	\cvsection{Education and academia experience}
	\begin{cventries}
		\cventry
		{Postdoc in Robotics and Computer vision}
		{CIIRC-CTU, IMPACT (Josef Sivic)}
		{2022 - current}
		{Prague, Czech Republic}
		{
			\begin{cvitems}{}
				\item Conducted research on object pose detection and tracking, torque-based optimal control for a robot manipulator, and VLAs benchmarking. Supervision of 5 Msc. and Bsc. students.
				\item BOP project: Maintainer of the object pose estimation benchmark for the BOP challenge 24 and 25 
				(6 new datasets included, 10x faster online leaderboard) and the open-source BOP toolkit. Participation to the R6D workshops (ECCV-24, ICCV-25). 
				\item Reviewer for TRO, IJCV, RAL, ICRA, IROS.
			\end{cvitems}
		}

		\cventry
		{PhD. in Robotics}
		{LAAS-CNRS}
		{2018 - 2022}
		{Toulouse, France}
		{	
			\begin{cvitems}{}
				\item Thesis: \textit{State estimation and localization of legged robots based on a-posteriori maximization}
				\item Supervisors: Nicolas Mansard, Joan Solà
			\end{cvitems}
		}

		\cventry
		{Master Thesis in Underwater Robotics}
		{Heriot-Watt University}
		{2018 (6 months)}
		{Edinburgh, UK}
		{
			\begin{cvitems}{}
				\item Thesis: \textit{Visual servoing and impedance control for an underwater robotics manipulator}
				\item Supervisor: Yvan Petillot
			\end{cvitems}
		}
		
		\cventry
		{MSc. in Operationnal Research}
		{ENAC and ISAE-SUPAERO}
		{2018}
		{Toulouse, France}
		{
			Courses in global deterministic, stochastic, and combinatory optimisation.
		}

		\cventry
		{Aerospace Engineering school}
		{ISAE-SUPAERO}
		{2014 - 2018}
		{Toulouse, France}
		{
			Courses in aircraft design, numerical simulation, computer science and related topics. Specialization on Robotics and Data Science.
			% \begin{cvitems}{}
			% 	\item Last year Robotics project: Fast trajectory generation for an autonomous car using memory of motion.
			% 	\item Last year DataScience project: Playing Flappy Bird with Deep Q-Learning.
			% 	\item Student Aerospace Challenge: won the Airbus Group Prize for our work on the "Preliminary design of a solid propulsion motor for a manned suborbital vehicle".
			% 	\item Supaero robotics club: participation to the 2016 robotics cup.
			% \end{cvitems}
		}

	\end{cventries}

	\cvsection{Industry experience}
	\begin{cventries}
		\cventry
		{Data analyst}
		{Activus Group}
		{2017 (5 months)}
		{Toulouse, France}
		{
			Computer network activity prediction and web scraping for job market analysis.
		}
	\end{cventries}
	\begin{cventries}
		\cventry
		{Full stack web developer}
		{Sfara}
		{2016 - 2017 (6 months)}
		{Hoboken NJ, USA}
		{
			Development of a car fleet analytics web site (Flask+Vuejs), internal tools creations.
		}
	\end{cventries}


	\cvsection{Selected Publications}
		\begin{itemize}[leftmargin=3ex, nosep, noitemsep]
			\setlength{\parskip}{0pt}
			\renewcommand{\labelitemi}{$\bullet$}  % $$ needed HERE !
			\item \publication
			{Ponimatkin G, Cífka M, Souček T, \textbf{Fourmy M}, Labbé Y, Petrik V, Sivic J.}
			{6D Object Pose Tracking in Internet Videos for Robotic Manipulation}
			{ICLR, 2025}
			\item \publication
			{Nguyen VN, Tyree S, Guo A, \textbf{Fourmy M}, Gouda A, Lee T, Moon S, Son H, Ranftl L, Tremblay J et al.}
			{BOP Challenge 2024 on Model-Based and Model-Free 6D Object Pose Estimation.}
			{CVPRW, 2025, Best Workshop Paper Award}
			\item \publication
			{Zorina K, Priban V, \textbf{Fourmy M}, Sivic J, Petrik V.}
			{Temporally Consistent Object 6D Pose Estimation for Robot Control}
			{RAL, 2025}
			\item \publication
			{Haffemayer A, Jordana A, \textbf{Fourmy M}, Wojciechowski K, Saurel G, Petrík V, Lamiraux F, Mansard N.}
			{Model Predictive Control Under Hard Collision Avoidance Constraints for a Robotic Arm}
			{Ubiquitous Robots, 2024}
			\item \publication
			{Sola J, Vallvé J, Casals J, Deray J, \textbf{Fourmy M}, Atchuthan D, et al.}
			{WOLF: A modular estimation framework for robotics based on factor graphs}
			{RAL, 2022}	
			\item \publication
			{\textbf{Fourmy M}, Flayols T, Léziart PA, Mansard N, Solà J.}
			{Contact Forces Preintegration for Estimation in Legged Robotics using Factor Graphs}
			{ICRA, 2021}
			\item \publication
			{\textbf{Fourmy M}, Atchuthan D, Mansard N, Sola J, Flayols, T.}
			{Absolute humanoid localization and mapping based on IMU Lie group and fiducial markers}
			{Humanoids, 2019}
		\end{itemize}

	\cvsection{Skills}
	\vspace{-0.3cm}
	%
	\begin{minipage}[t]{.49\textwidth}
		\begin{cvskills}
			\cvskill{Programming}{Python, C++, Javascript}
			\cvskill{Datascience}{Pytorch, Scikit-learn, SQL}
			\cvskill{Robotics}{ROS2, Pinocchio, Croccodyl}
			\cvskill{Tools}{Git, Docker, \LaTeX, Linux}
			\cvskill{Web}{Django, HTML, CSS}
		\end{cvskills}
	\end{minipage}
	%
	\begin{minipage}[t]{.49\textwidth}
		\begin{cvskills}
			\cvskill{Languages}{French (native), English (fluent)}
			\cvskill{Interests}{Music, climbing}
		\end{cvskills}
	\end{minipage}
\end{document}
