\documentclass[11pt, a4paper, final]{resume}

\usepackage{setspace}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

% for debugging purposes
%\overfullrule=5pt

\renewcommand{\baselinestretch}{1}

\begin{document}

	\header
		{Médéric}
		{Fourmy}
		{8 Grande Rue Saint Michel, 31400 Toulouse - France}
		{mederic.fourmy@supaero.isae.fr}
		{+33672745468}

	\cvsection{Education}
	\begin{cventries}
		\cventry
		{ISAE-SUPAERO}
		{Aerospace engineering school, Msc 2 in Robotics and Data Science}
		{Toulouse, France}
		{Sept. 2014 - 2018}
		{}
		\cventry
		{ENAC and ISAE-SUPAERO}
		{Msc 2 in Operationnal Research}
		{Limoges, France}
		{2018}
		{}
		\cventry
		{Lycée Gay-Lussac}
		{Advanced undergraduate course in Mathematics, Physics and Chemistry}
		{Limoges, France}
		{2011 - 2014}
		{}
	\end{cventries}

	\cvsection{Work experience}
	\begin{cventries}
		\cventry
		{Activus Services}
		{Data science intern}
		{Limoges, France}
		{2011 - 2014}
		{
			\begin{cvitems}{}
				\item Computer network activity prediction with Machine Learning using Python and Spark
				\item Developed a French job market analysis tool including a web Scraper
			\end{cvitems}
		}
		\cventry
		{Sfara}
		{Full stack web developer and data analyst intern}
		{Hoboken NJ, USA}
		{Sept. 2016 - Mars 2017}
		{
			\begin{cvitems}{}
				\item Participated to the development of the analytics web site on the back-end (Flask) and front-end (Vuejs)
				\item Designed and implemented a metrics monitoring board being updated in real-time with Web Sockets
				\item Created internal tools, including an automatic weekly report generation script and a SQL query generation interface
			\end{cvitems}
		}
	\end{cventries}


	\cvsection{Projects}
	\begin{cventries}
		\cventry
		{Third year innovation project}
		{Fast trajectory generation for an autonomous car using memory of motion}
		{Toulouse, France}
		{Oct. 2017 - Mars 2018}
		{
			\begin{cvitems}{}
				\item DOING
				\item Doing that
			\end{cvitems}
		}
		\cventry
		{Student aerospace challenge}
		{Manned suborbital vehicle propulsion system design}
		{Toulouse, France}
		{Sept. 2016 - Mars 2017}
		{
			Preliminary design of a solid propulsion motor for a manned suborbital vehicle. Worked as part of the Supaero Propulsion team and presented our
			results during the Suborbital Day at the Paris Air and Space Museum. Won the Airbus Group Price.
		}
		\cventry
		{Second year research project}
		{Computational Fluid Dynamics}
		{Toulouse, France}
		{Sept. 2016 - Mars 2017}
		{
			Assessment of the influence of upstream flow distortions on the efficiency of a
			reversible cooling fan thanks to numerical computation for Safran-Technofan
		}
	\end{cventries}


	\cvsection{IT}
	\begin{cvskills}
		\cvskill{Programming}{Python, C++, Javascript, Java, Matlab}
		\cvskill{Datascience}{Scikit-learn, Pyspark, Tensorflow, Keras}
		\cvskill{DevOps}{Git, Docker, Jenkins, Kafka}
		\cvskill{Web}{Flask, Vuejs, HTML, CSS}
		\cvskill{Office automation}{Latex, MS Office, Weasyprint}
	\end{cvskills}

	\cvsection{Languages}

	\cvlanguages
	{French}{ \fiveoverfive }
	{English}{ \fourandahalfoverfive }
	{Portuguese}{ \twooverfive }
	{}{}

	\cvsection{Extra curricular activities}
	\begin{cvskills}
		\cvskill{Associations}{DirectoR of the Supaero music club, robotics club}
		\cvskill{Music}{bass, guitar, harp, improvisation}
		\cvskill{Sport}{Badminton}
	\end{cvskills}

\end{document}
